New Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations

### 2019-12-24 nontex/install/linux/fn_ubuntu.Rmd
new gist for atom sync, latex installation
update installation better linux R

@@

```{bash}
# could be saved in current folder: pwd
# could be saved in download folder: ~/Downloads
wget https://repo.anaconda.com/archive/Anaconda3-2019.10-Linux-x86_64.sh
# install file
bash "Anaconda3-2019.10-Linux-x86_64.sh"
# refresh
source ~/.bashrc
# show all installed packages under current envir
conda list
# see where key files are installed
which python
which conda
# use conda-forge as main channel and update all
conda config --add channels conda-forge
conda update --all
```

>>>>

- *personal access token*: b36b4d26ff2b5b626a1d7f66e3bc60c582a85c21
- *Gist id*: a883a7ba62661dbe9b907d24b651b780

@@

```{bash}
# To remove conda Fully
rm -rf ~/anaconda3

# could be saved in current folder: pwd
# could be saved in download folder: ~/Downloads
wget https://repo.anaconda.com/archive/Anaconda3-2019.10-Linux-x86_64.sh
# install file
bash "Anaconda3-2019.10-Linux-x86_64.sh"
# refresh
source ~/.bashrc

# show all installed packages under current envir
conda list
# see where key files are installed
which python
which conda
# use conda-forge as main channel and update all
/* conda config --add channels conda-forge */
conda update --all
```

Additional statistics and related models to install:

```{r}
conda install -y statsmodels datashape seaborn
# conda install statsmodels
# conda install datashape
# conda install seaborn

conda install -c conda-forge -y interpolation awscli
# conda install -c conda-forge interpolation
# conda install -c conda-forge awscli

conda install -c anaconda -y boto3

# conda install -c r r-irkernel
```

### 2019-12-24 nontex/install/windows/fn_installations.Rmd
update installation better linux R

@@

```{bash}
where anaconda
# C:/ProgramData/Anaconda3/Scripts/anaconda.exe
where python
# C:/ProgramData/Anaconda3/python.exe
where jupyter
# C:/ProgramData/Anaconda3/Scripts/jupyter.exe
where jupyter-kernelspec
# if R installed already
where r

@@

```{bash}
# # if there are bugs
# conda clean --packages
# use conda-forge as main channel, more updated packages
conda config --get channels
conda config --add channels conda-forge
conda config --get channels
# remove conda-forge from channels (do so for main env install)
conda config --remove channels conda-forge
# normal update
conda update --all
```

@@

```{bash}
# Once atom is installed, can use apm to install packages
apm install hydrogen
# Inside Conda open up atom
atom
# open up any py from from within, try 1+1, does it work?
```

## Additional Packages

```{r}
conda install statsmodels datashape seaborn
# conda install statsmodels
# conda install datashape
# conda install seaborn

conda install -c conda-forge interpolation awscli
# conda install -c conda-forge interpolation
# conda install -c conda-forge awscli

conda install -c anaconda boto3

# conda install -c r r-irkernel
```

@@

## Fully uninstall r

open up RStudio, and see where paths are.
also open up R from command prompt, see where paths are.

@@

@@

```{bash}
# Go to get latesdebian latest r sources.list
cat /etc/apt/sources.list
# Install this First (should already be installed)
sudo apt install dirmngr

@@

# Also install these, otherwise r-packages do not install:
sudo apt-get install libcurl4-openssl-dev
sudo apt-get install libssl-dev
```

```{r}
# Install R-tools, RTOOLS is for WINDOWS
install.packages("installr")
library("installr")
install.Rtools()
# c:/Rtools/bin;
# c:/Rtools/mingw_32/bin;
# c:/Rtools/mingw_64/bin;

# main packagevps
# tidymodel installation on linux difficult
install.packages(c("tidyr", "tidyverse", "tidymodels"))
# development packages
install.packages(c("devtools", "irkernel", "pkgdown", "roxygen2"))
# other packages
install.packages(c("AER", "minpack.lm", "knitr", "kableExtra", "matlab"))

# Install my package
devtools::install_github("fanwangecon/R4Econ")

# Kernel
install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
devtools::install_github('IRkernel/IRkernel')
IRkernel::installspec()
```

@@

```{bash}
# Set up Channel, for R, to get latest r-packages
# do not set-up channels to prioritize conda-forge for main env.
conda config --add channels conda-forge
# install key r packages within a r-environment
conda env remove -n r_env
conda create -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2
# see all installed environments
conda env list
# activate an environment to use it, if in base, r does not exist, isolated in r_env
conda activate r_env
# see packages in environment
conda list
# to quit
conda deactivate
```

@@

This did not work in windows, *tidymodels* failed to install. Perhaps because of directory issues. *tidymodels* required *rstanarm*, and *rstanarm* failed to install.

```{bash}
### One line
conda install -c conda-forge r-aer r-minpack.lm r-knitr r-kableExtra r-matlab
# conda install -c conda-forge r-rstanarm

#######################################
### Estimation
#######################################
# Estimation Tools
# tidymodels does not work fron conda install
# Linear Regression Package
# https://anaconda.org/conda-forge/r-aer
# Nonlinear Regression Package
# https://anaconda.org/conda-forge/r-minpack.lm
conda install -c conda-forge r-aer r-minpack.lm
# enter r and use devtools
# install.packages("tidymodels")

#######################################
### Visualiation
#######################################
conda install -c conda-forge r-knitr r-kableExtra

#######################################
### Utilities
#######################################
# Allowing for Invoking Matlab Files from Inside R
conda install -c conda-forge r-matlab
```

@@

- [Proton VPN](https://protonvpn.com/): unlimited usage free version available.

@@

- 7-zip

>>>>

To install conda in Debian, follow [these instructions](https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html).

@@

```{bash}
# To remove conda Fully
rm -rf ~/anaconda3

where anaconda
# C:/ProgramData/Anaconda3/Scripts/anaconda.exe
where python
# C:/ProgramData/Anaconda3/python.exe
where jupyter
# C:/ProgramData/Anaconda3/Scripts/jupyter.exe
where jupyter-kernelspec
# if R installed already
where r

@@

```{bash}
# # if there are bugs
# conda clean --packages
# use conda-forge as main channel, more updated packages
conda config --get channels
conda config --add channels conda-forge
conda config --get channels
# remove conda-forge from channels (do so for main env install)
conda config --remove channels conda-forge
# normal update
conda update --all

# install additional packages
conda install -y statsmodels datashape seaborn
conda install -c conda-forge -y interpolation awscli
conda install -c anaconda -y boto3
```

@@

```{bash}
# Once atom is installed, can use apm to install packages
apm install hydrogen
# Inside Conda open up atom
atom
# open up any py from from within, try 1+1, does it work?
# also use script, try ctrl + shift + b, run whole file (not hydrogen)
```

@@

## Fully Uninstall r

Open up RStudio, and see where paths are.
also open up R from command prompt, see where paths are.

@@

For Linux:

- if used apt-get to install, R installed under main user drive, deactivate conda, and check which conda

```{bash}
# Exit Conda
conda deactivate
# where is R installed outside of Conda
which R
# /usr/bin/R
# To remove all
sudo apt-get remove r-base
sudo apt-get remove r-base-core

# Inside Conda base
conda activate
# Conda r_env
conda activate r_env
# Where is it installed?
which R
# /home/wangfanbsg75/anaconda3/bin/R
conda uninstall r-base
```

@@

```{bash}
# If inside Debian, due to some tidymodel install issues, do this`
conda install -c r r
conda install -c r r-essentials
conda install -c r r-igraph
conda install -c conda-forge igraph

# Go to get latesdebian latest r sources.list
cat /etc/apt/sources.list
# Install this First (should already be installed)
sudo apt install dirmngr

@@

# Also install these, otherwise r-packages do not install
# libxml2 seems need for tidymodels
sudo apt-get install libcurl4-openssl-dev
sudo apt-get install libssl-dev
sudo apt-get install libxml2-dev
```

Which R?

- *export RSTUDIO_WHICH_R=/usr/bin/R*
- *export RSTUDIO_WHICH_R=/home/wangfanbsg75/anaconda3/bin/R*

```{r}
# Can enter R from Command Prompt Conda ENV, much faster than from r-studio
# Install R-tools, RTOOLS is for WINDOWS
install.packages("installr")
library("installr")
install.Rtools()
# c:/Rtools/bin;
# c:/Rtools/mingw_32/bin;
# c:/Rtools/mingw_64/bin;

# main packagevps
# tidymodel installation on linux difficult
install.packages(c("tidyverse", "tidymodels", "tidyr"))
# development packages
install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
# other packages
install.packages(c("AER", "minpack.lm", "knitr", "matlab"))

# Install my package, need to prepare package to work for ubuntu
# if install does not work, load locally
devtools::install_github("fanwangecon/R4Econ")

# Kernel
install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
IRkernel::installspec()
```

@@

```{bash}
# outside of conda, install some depencies
sudo apt-get install libcurl4-openssl-dev
sudo apt-get install libssl-dev
sudo apt-get install libxml2-dev

# install key r packages within a r-environment
conda env remove -n r_env
# start empty environment
conda create -n r_env
# activate env and check, nothing yet
conda activate r_env
conda list

# check channel and add env specific channel
conda config --get channels
# to get latest r, use conda-forge, which has more recent Rs
# conda config --env --add channels conda-forge
# channels for base
conda config --get channels
# channels for cur env
conda config --get channels --env

# install files
conda install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y

# trouble with igraph installation, install here from conda
# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2
conda install -n r_env -c r r-igraph
conda install -n r_env -c conda-forge igraph
conda install -n r_env -c r r-rstantools r-rstan r-rstanarm -y

# see all installed environments
conda env list
# activate an environment to use it, if in base, r does not exist, isolated in r_env
conda activate r_env
# see packages in environment
conda list
# to quit
conda deactivate
```

@@

*tidymodel* has installation issues sometimes.

In *r_env*, type in *R*, and then install from inside terminal's R:

```{bash}
# enter into env
conda activate r_env
# enter R or type in rstudio
# sicne R is only install inside r_env, has to enter rstudio from r_env
R
rstudio

# main packagevps
# tidymodel installation on linux difficult
install.packages(c("rstantools", "rstan", "rstanarm"))
install.packages(c("tidyr", "tidyverse", "tidymodels"))

# tidymodels
# development packages
install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
# other packages
install.packages(c("AER", "minpack.lm", "knitr", "matlab"))

# Install my package, need to prepare package to work for ubuntu
# if install does not work, load locally
devtools::install_github("fanwangecon/R4Econ")

# Kernel
install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
IRkernel::installspec()
```

@@

- [Proton VPN](https://protonvpn.com/): unlimited usage free version available.
- Express VPN

@@

- 7-zip
- evernote
- keepass
